Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-17 doc/PRF2022/PRF_main.tex
updated fig0, supplementary reference

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)-(b) show the average strain increase for bilayer, vesicle BL,
  multilamellar, and striated JP structures under a shear flow and a TG flow, respectively.
Panel (c)-(d) show the average alignment of four JP structures under a shear flow and a TG flow, respectively. 
Each snapshot of panels (e)-(l) contains the configurations of the JP structure using a specific type of boundary bondition without ruptures and the backgroud curves indicate the velocity streamlines.}
\end{figure}
%
We subjected the Type I, II, and III JP phases to background flows and measured 
their material response.  The background flows were a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
and vertical directions, respectively.
In both cases, $\dot \gamma$ is the shear rate.
In \eqref{eq:tg_flow}, $\lambda$ is the cell-size parameter.

@@

The shear flow replicates the motion of a fluid between two parallel, moving plates
excluding wall effects.  In TG flow, the flow pattern
consists of an array of counter rotating cells each with size 
$2\pi \lambda \times 2\pi \lambda$.  Throughout, we use $\lambda = 2$ nm
so that the JP phases occupy about nine cells.  To compare shear
on equal terms, the flow rate $\lambda \dot \gamma$  
was chosen for \eqref{eq:tg_flow} so that it has the same
rate of viscous dissipation per area as for \eqref{eq:sh_flow}.
In other words, 
$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
is the same for 
$\uu = \uu_{\infty}^{\text{sh}}$ as for 
$\uu = \uu_{\infty}^{\text{TG}}$
when integrated over a $TG$ cell $A$.

@@

Figure \ref{fig:s2esummary} (e)--(l) show the typical streamlines
for JP phases in background flow.  Although the plots only show
the region near the JP phases, the fluid velocity $\uu$ and 
order parameter $u$ are solved for in all of $\mathbb{R}^2$.
Moreover, $\uu$ satisfies the rigid boundary condition at 
every JP-fluid interface i.e., the particles interact with the local
flow field and are not merely carried by background flow.

The simulation setup consisted of placing each of the three JP phases
in either a shear or TG background flow and then solving for the 
particle trajectories in time.  A total of $500$ steps were solved
for with $\Delta t = 2$ ns, yielding time courses for various 
$\dot \gamma$ up to $T = 1$ $\upmu$s.  We then post-processed the trajectories
to infer free energy $F$, alignment order $S_2$, and strain $E$.     
\todo[inline]{Reference the supplementary material here.}

\subsection{Strain and alignment}
The plots reveal highly distinct material responses from each phase.
Figure \ref{fig:s2esummary} (a) and (b) show the time-averaged
strain $\frac{1}{T}\int_0^T E \,\dif t$ over a broad
range of shear rates.  Strain $E$
measures the non-rigid-body deformation relative to the initial state
and expectedly increases with shear rate.
The greatest increase occurs with the Type I amphiphiles, 
suggesting that this phase has the lowest elastic modulus
(squares). In comparison, 
the  striated phase consisting of  Type III polar JP is
basically rigid (triangles).

@@

\subsection{Free energy}
Figure \ref{fig:fsummary} plots the time-averaged
relative free energy $\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$ is 
\eqref{eq:free_energy2} at $t = 0$.  The 
greatest increase occurs with the Type II 
multilamellar phase, with the other phases 
showing a moderate change in a few \KBT\,nm$^{-1}$.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{RheologySummary.pdf}
\end{center}
\caption{\label{fig:rheologysummary}
  Rheology of Type I, II, and III phases.
  Panel (a) shows that bilayer phases  behave as a Newtonian fluid.
  Panel (b) provides that the multilamellar phase shows a near shear thinning behaviour.
  A pseudoplastic behaviour of deformation in striated phases is shown in panel (c). }
\end{figure}
\subsection{Rheology}
So far, we have considered static material properties, namely
constant strains maintained by an external force provided by   
background flow. Now we consider dynamic material properties.
Specifically, we look at the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that 
the shear flow $\uu_{\infty}^{\text{sh}}$
simulations correspond to a complex fluid within a drag plate
rheometer where the shear stress is set by $\mu \dot\gamma$  
and the observed, sample shear rate is $\dot E$. 
The definitions carry over to the TG flow case directly. 
Also, as a practical consideration,
the rotation of non-isotropic JP phases in the background 
flow leads to oscillation in the strain time courses 
making systematic fitting challenging (see 
Supplementary Material Figures \ref{fig:veshraw}--\ref{fig:sttgraw}). 
The integral in \eqref{eq:strainrate} averages out these oscillations
and gives physically meaningful values.

>>>>

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
  Panel (a)-(b) show the average strain increase for bilayer, vesicle BL,
  multilamellar, and striated JP structures under a shear flow and a TG flow, respectively.
Panel (c)-(d) show the average alignment of four JP structures under a shear flow and a TG flow, respectively. 
Each snapshot of panels (e)-(l) contains the configurations of the JP structure using a specific type of boundary bondition without ruptures and the backgroud curves indicate the velocity streamlines.}
\end{figure}
%
We subjected the Type I, II, and III JP phases to background flows and measured 
their material response.  The background flows were a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
and vertical directions, respectively.
The shear flow replicates the motion of a fluid between two parallel,
moving plates excluding wall effects.
In TG flow, $\lambda$ controls the size of the
$2\pi \lambda \times 2\pi \lambda$ TG cells.
Throughout, we use $\lambda = 2$ nm
so that the JP phases occupy about nine cells.

In both cases, $\dot \gamma$ is the shear rate.
The flow rate $\lambda \dot \gamma$  
was chosen so that \eqref{eq:tg_flow} has the same
rate of viscous dissipation per area as for \eqref{eq:sh_flow}.
In other words, 
$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
is the same for 
$\uu = \uu_{\infty}^{\text{sh}}$ as for 
$\uu = \uu_{\infty}^{\text{TG}}$
when integrated over a $TG$ cell $A$.

@@

@@

Figure \ref{fig:s2esummary} (e)--(l) show the typical streamlines
for JP phases in background flow.  Although the plots only show
the region near the JP phases, the fluid velocity $\uu$ and 
order parameter $u$ are accounted for in all of $\mathbb{R}^2$.
Moreover, $\uu$ satisfies the rigid boundary condition at 
every JP-fluid interface i.e., the particles interact with the local
flow field and are not merely carried by background flow.

The simulation setup consisted of placing each of the 
phases in either a shear or TG background flow and then solving for the 
particle trajectories in time. In each setup, we solved for $500$ time steps 
with $\Delta t = 2$ ns, yielding time courses for $t \in [0, T]$, $T = 1$ $\upmu$s.
We then post-processed the trajectories.

Supplementary Figures~\ref{fig:veshraw}--\ref{fig:sttgraw}
contain the fully-resolved time courses for free energy $F$,
alignment order $S_2$, and strain $E$. The eight setups
correspond to the four JP phases---bilayer, vesicle BL, multilamellar,
and striated---and two background flows---shear and TG,
and the data are plotted with the same ordinate to facilitate
comparisons between simulation setups.  Each setup considers
a range of shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.

The fully-resolved time courses
in Supplementary Figures~\ref{fig:veshraw}--\ref{fig:sttgraw}
contain significant oscillations due to the particle-based formulation
and tumbling inherent to the background flows.  To extract meaningful
data, we further postprocessed the $F$, $S_2$, $E$ curves by taking
their time averate over the interval $t \in [0, T]$.

\subsection{Strain and alignment}
\label{sec:strain-alignment}
The plots reveal highly distinct material responses from each phase.
Figure \ref{fig:s2esummary} (a) and (b) show the time-averaged
strain $\frac{1}{T}\int_0^T E \,\dif t$ over a broad
range of shear rates.  Strain $E$
measures the non-rigid-body deformation relative to the initial state
and expectedly increases with shear rate.
The greatest increase occurs with the Type I amphiphiles, 
suggesting that this phase has the lowest elastic modulus
(squares). In comparison, 
the  striated phase consisting of  Type III polar JP is
basically rigid (triangles).

@@

\subsection{Free energy}
\label{sec:free-energy}
Figure \ref{fig:fsummary} plots the time-averaged
relative free energy $\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$ is 
\eqref{eq:free_energy2} at $t = 0$.  The 
greatest increase occurs with the Type II 
multilamellar phase, with the other phases 
showing a moderate change in a few \KBT\,nm$^{-1}$.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{RheologySummary.pdf}
\end{center}
\caption{\label{fig:rheologysummary}
  Rheology of Type I, II, and III phases.
  Panel (a) shows that bilayer phases  behave as a Newtonian fluid.
  Panel (b) provides that the multilamellar phase shows a near shear thinning behaviour.
  A pseudoplastic behaviour of deformation in striated phases is shown in panel (c). }
\end{figure}

\subsection{Rheology}
\label{sec:rheology}
So far, we have considered static material properties, namely
constant strains maintained by an external force provided by   
background flow. Now we consider dynamic material properties.
Specifically, we look at the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that 
the shear flow $\uu_{\infty}^{\text{sh}}$
simulations correspond to a complex fluid within a drag plate
rheometer where the shear stress is set by $\mu \dot\gamma$  
and the observed, sample shear rate is $\dot E$. 
The definitions carry over to the TG flow case directly. 
Also, as a practical consideration,
the rotation of non-isotropic JP phases in the background 
flow leads to oscillation in the strain time courses 
making systematic fitting challenging (see 
Supplementary Material Figures \ref{fig:veshraw}--\ref{fig:sttgraw}). 
The integral in \eqref{eq:strainrate} averages out these oscillations
and gives physically meaningful values.

### 2023-03-17 doc/PRF2022/Supplementary.tex
updated fig0, supplementary reference

\sloppy
\section{Movie Captions}\mbox{} \\

@@

>>>>

\section{Movie Captions}\mbox{} \\

@@

\section{Raw Data}
The following figures plot the fully resolved simulation time-courses
organized in terms of the bilayer, vesicle BL, multilamellar, and striated JP phases
under shear flow (Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:stshraw})
and under TG flow (Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
Throughout, panels (a) are for relative free energy $F - F_0$,
panels (b) for alignment $S_2$, and panels (c) for strain $E$ (as a percentage). 
A common ordinate is used for each of the respective panels to facilitate
comparison between data sets. 
\newpage

\begin{figure}[h!]
\begin{center}
\textbf{\textsc{Shear Flow cases}}\par\medskip
\textbf{Type I, bilayer phase under shear flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/ULShRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, bilayer phase under shear flow with choices of shear rates $\dot\gamma=0.013$ -- $0.075$ ns$^{-1}$.
%The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:ulshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under shear flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeShRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, bilayer phase under shear flow with choices of shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
The JP type is the same as for Supplementary Figure \ref{fig:ulshraw} but with a
ring-shaped, rather than disordered, bilayer for initial configuration.  
%A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:veshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type II, multilamellar phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/MLShRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type II, multilamellar phase under shear flow with choices of shear rates $\dot\gamma=0.025$ -- $0.075$ ns$^{-1}$.
%A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mlshraw}
\end{figure}

\begin{figure}[h!]
\textbf{Type III, striated phase under shear flow}\par\medskip
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/StShRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type III, striated phase under shear flow with choices of shear rates $\dot\gamma=0.01$ -- $0.07$ ns$^{-1}$.
%A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:stshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{\textsc{TG Flow Cases}}\par\medskip
\textbf{Type I, bilayer  phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/ULTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, bilayer phase under TG flow with choices of shear rates $\dot\gamma=0.013$ -- $0.05$ ns$^{-1}$.
%A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:ultgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type I, vesicle BL phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/VeTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type I, vesicle bilayer phase under TG flow with choices of shear rates $\dot\gamma=0.005$ -- $0.044$ ns$^{-1}$.
The JP type is the same as for Supplementary Figure \ref{fig:ultgraw} but with a
ring-shaped, rather than disordered, bilayer for initial configuration.  
%A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:vetgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type II, multilamellar phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/MLTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type II, multilamellar phase under TG flow with choices of shear rates $\dot\gamma=0.025$ -- $0.069$ ns$^{-1}$.
%A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:mltgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\textbf{Type III, striated phase under TG flow}\par\medskip
\includegraphics[width=\textwidth]{SMFigures/StTGRaw.pdf}
\end{center}
\caption{
Relative free energy $F - F_0$,
alignment $S_2$, and strain $E$ for
Type III, striated phase under TG flow with choices of shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
%A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
}
\label{fig:sttgraw}
\end{figure}
